Bird beak's elaboration and exploration

### 2021-11-01 Analysis/02.1-shapespace_allbirds_lvl_superorder_order.Rmd
removed unused data

```{r}
## Preparing the model files
model_list <- list()
class(model_list) <- c("beer", "mini.chains")
models_path <- "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/cluster/"
## Loading all models
for(file in list.files(models_path)) {
    load(paste0(models_path, file, collapse = "/"))
    model_list[[length(model_list)+1]] <- model[[1]]
}

## Combining the model files
shapespace_allbirds_lvl_superorder_order <- combine.mini.chains(model_list)

@@

## Saving the results
save(shapespace_allbirds_lvl_superorder_order, file = "../Data/processed/shapespace_allbirds_lvl_superorder_order.rda")

>>>>

```{r}
## Preparing the model files
model_list <- list()
class(model_list) <- c("beer", "mini.chains")
models_path <- "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/cluster/"
## Getting all the model files
model_files <- list.files(models_path, pattern = ".rda")
## Get the first model
load(paste0(models_path, model_files[1], collapse = "/"))
print(model_files[1])
## Clean the bits that are not going to be used (but are huge)
model[[1]][c("error.term", "family", "y.additional", "ginverse", "ZR")] <- NULL
## Update the model list
model_list[[length(model_list)+1]] <- model[[1]]
model <- NULL
model_files <- model_files[-1]

## Get the subsequent models and merge them as we go
while(length(model_files) != 0) {
    load(paste0(models_path, model_files[1], collapse = "/"))
    print(model_files[1])
    ## Clean the bits that are not going to be used (but are huge)
    model[[1]][c("error.term", "family", "y.additional", "ginverse", "ZR")] <- NULL
    ## Update the model list
    model_list[[length(model_list)+1]] <- model[[1]]
    ## Merge the models (overwrite the model list)
    model_list <- list(combine.mini.chains(model_list))
    ## DEBUG
    print("model list size:")
    print(format(object.size(model_list), units = "MB"))
    model <- NULL
    model_files <- model_files[-1]
}

## Combining the model files
shapespace_allbirds_lvl_superorder_order <- model_list[[1]]

@@

## Saving the results
save(shapespace_allbirds_lvl_superorder_order, file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order.MCMCglmm")
